How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in the Pacific Pond Turtle (\textit{Emys marmorata})

### 2015-09-08 doc/second_tab.tex
abstract, jim ken comments, need new graphs

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Wed Aug 26 12:02:25 2015
\begin{table}[ht]
  \centering
  \begin{tabular}{ l r r r }
    \hline
    & \# predictors & In-sample AUC & Out-of-sample AUC \\ 
    \hline
    random forest &   11 & 1.000 & 0.999 \\ 
    linear discriminate analysis &   10 & 1.000 & 1.000 \\ 
    multinomial logistic regression &    6 & 1.000 & 0.998 \\ 
    \hline
  \end{tabular}
  \caption{Results from classification model estimates of the secondary, multi-species dataset. Comparison of in-sample and out-of-sample AUC of the best performing model, along with the number of predictors. AUC values range between 0.5 (no better than random) and 1 (perfect classification).}
  \label{tab:second_res}
\end{table}

>>>>

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Tue Sep  8 12:03:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & npred & ii.auc & oo.auc \\ 
  \hline
RF &   11 & 1.000 & 1.000 \\ 
  LDA &   10 & 1.000 & 1.000 \\ 
  MnL &    4 & 1.000 & 1.000 \\ 
   \hline
\end{tabular}
\label{tab:second_res}
\end{table}
